Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Fix typo

Our algorithm generalizes randomized tree expansion strategies, introduced in both \cite{HsuLat99c} and
\cite{kuffner00rrtconnect} to constrained motion planning problems. Next subsection will recall the structure of the RRT algorithm,
a popular randomized motion planning algorithm. 
{\bf Our method could be applied to any randomized sampling planning method, such
as RRT\up{*} \cite{Karaman01062011}, which is slower than RRT but generates optimal
paths.}

>>>>

Our algorithm generalizes randomized tree expansion strategies, introduced in both \cite{HsuLat99c} and
\cite{kuffner00rrtconnect} to constrained motion planning problems. Next subsection will recall the structure of the RRT algorithm,
a popular randomized motion planning algorithm. 
{\bf Our method could be applied to any randomized sampling planning method, such
as RRT\textsuperscript{*} \cite{Karaman01062011}, which is slower than RRT but generates optimal
paths.}
